\documentclass{article}
\usepackage{color}
\usepackage{tikz}
\usepackage{float}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{syntax}
\usepackage{csquotes}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  numbers=left,
  stepnumber=1,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numberstyle=\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2,
  moredelim=**[is][\color{red}]{@}{@},
}

\setlength{\grammarindent}{12em}

%\renewcommand{\lstlistingname}{Algorithm}
%\newcommand{\tablerow}[4]{ #1 & #2 & #3 & #4\\}
\newcommand{\n}[0]{\\[\baselineskip]}
%\newcommand{\qa}[2]{\textbf{Q:} #1 \\ \textbf{A:} #2}
%\newcommand{\argument}[4]{\textbf{#1:} #2 \\ \textbf{#3:} #4}

\title{CS4303 Particle Command Report}
\author{Sizhe Yuen}

\begin{document}

\maketitle

\section{Introduction}
In this practical we were tasked to implement the video game \textit{Particle Command}, which is a variant on missile command where the particles are blasted away from the explosion rather than being destroyed. In my game, I have implemented all the features in the practical specifications as well as some additional features.
\n
TODO RUN INSTRUCTIONS

\section{Game features}

\subsection{Basic}
\subsubsection*{Meteors}
The particles falling are implemented in the \texttt{Meteor} class. They spawn from a random location at the top of the screen and have a random initial velocity. This initial random velocity goes from \texttt{-2f} to \texttt{2f} in the x direction and from \texttt{0} to \texttt{3f} in the y direction. The random y velocity makes some particles come down faster than others to make the game a bit more interesting. They do not have a random negative y velocity because all particles not in the screen are destroyed. 

\subsubsection*{Cities}
There are five locations where the cities are placed on the ground of the play area. These are static and do not change. This was done for simplicity and a fair balance so there are not occasional games where the cities are very far away, making the game more difficult. 

\subsubsection*{Explosions}
All particles can create explosions when they are destroyed as it is an abstract method all \texttt{Particle} subclasses must implement. In my game, both the meteors and player missiles create explosions. The explosion radius is based off of the particle's initial radius, increasing with each time step until they've reach the end of their lifespan. Any particles caught in the blast radius are blown away with an \texttt{Explosive} force. 

\subsubsection*{Player missiles}
The player missiles fire from the center of the ground. Their velocity is normalised so it takes a bit of planning to properly defend the cities that are further away. The missile explode either when they reach their destination - the position of the mouse cursor when the missile was fired - or when they collide with a meteor during their trajectory. 


\subsubsection*{Waves}
The game is organised into waves. At the beginning of each wave, the number of missiles the player has is increased. Each wave has increasing difficulty as more meteors are spawned. Every few waves, the player is rewarded with a black hole or forcefield to help them survive. However, every few waves a bomber also comes which makes the game more difficult.


\subsection{Extension}

\subsubsection*{Black holes}
To add the force of gravitational attraction to the game, I added a special missile that player's can shoot which would create a black hole. The black holes apply gravitational attraction to all meteors on screen and because they are intentionally much heavier than the meteors, most will be sucked into the black hole and destroyed. Meteors that are further away may be affected less.
\n
The black holes only last for a short while before disappearing. This means that if a meteor was being accelerated towards it but did not get sucked in, even though it no longer has the gravitational force acting on it, it may have been accelerated to a very fast velocity and crash down onto a player's city. This makes the use of black holes more strategic and a double edged sword if used improperly. 
\subsubsection*{Forcefield}
Unlike explosions, forcefield use a different kind of force to repel particles which makes them a more global and powerful tool to deflect meteors compared to missiles. Instead of applying an explosive force to knock the meteors away, forcefields use the opposite force of gravitational attraction. The meteors are repulsed away from the forcefield by multiplying the force of gravitational attraction by -1. 
\n
The button for using forcefields is the middle mouse button.
\subsubsection*{Bombers}

\subsubsection*{Shop}



\section{Design}


\subsection{Physics}


\subsection{Collision}
 

\subsection{State management}




\end{document}